PANCHANGE_descriptives

### 2020-11-06 PANCHANGE_exclusion_descriptives.Rmd

#Impute no change prepandemic scores

@@

```{r Correlation prep chunk}
# Select items for correlation matrix
prepan_retro_items <- c(
    "gad.sum_score_prepan",
    "gad.sum_score_retro", 
    "phq.sum_score_prepan",
    "phq.sum_score_retro"
)

>>>>

#HR

```{r Accuray scores for gad: worse/better than pre-pandemic}

dat.raw$gad.pandemic.change.group <- ifelse(dat.raw$gad.pandemic_felt_feelings_numeric <3,1,
                                           ifelse(dat.raw$gad.pandemic_felt_feelings_numeric > 3,2,0))

dat.raw$gad.pandemic.change.group <- factor(dat.raw$gad.pandemic.change.group,
                                           levels = c(1,0,2),labels = c("Worse","No change","Better"))

dat.raw <- dat.raw %>%
    mutate(gad.change.accurate = case_when(dat.raw$gad.pandemic.change.group == "Better" &
                                             dat.raw$gad.diff_score_base_prepan < 0 ~1,
                                           dat.raw$gad.pandemic.change.group == "Worse" &
                                             dat.raw$gad.diff_score_base_prepan > 0 ~ 1,
                                           dat.raw$gad.pandemic.change.group == "Better" &
                                             dat.raw$gad.diff_score_base_prepan > 0 ~ 0,
                                           dat.raw$gad.pandemic.change.group == "Worse" &
                                             dat.raw$gad.diff_score_base_prepan < 0 ~ 0))

dat.raw <- dat.raw %>%
    mutate(gad.change.retro.accurate = if_else(dat.raw$gad.pandemic.change.group == "Better" &
                                             dat.raw$gad.diff_score_retro_prepan == 0 |
                                             dat.raw$gad.pandemic.change.group == "Worse" &
                                             dat.raw$gad.diff_score_retro_prepan == 0, 1, 3 ))
dat.raw <- dat.raw %>%
  mutate(gad.change.retro.accurate = if_else(dat.raw$gad.pandemic.change.group == "Better" &
                                             dat.raw$gad.diff_score_retro_prepan >= -3 &
                                             dat.raw$gad.diff_score_retro_prepan <= 3 &
                                             dat.raw$gad.change.retro.accurate_temp != 1 |
                                             dat.raw$gad.pandemic.change.group == "Worse" &
                                             dat.raw$gad.diff_score_retro_prepan >= -3 &
                                             dat.raw$gad.diff_score_retro_prepan <= 3 &
                                             dat.raw$gad.change.retro.accurate_temp != 1,  2, gad.change.retro.accurate))

#SB - Impute no change prepandemic scores

I interpreted the presence of an NA in the retrospective score as an indicator of saying "no change" in their baseline scores. Hence, if this was the case, I imputed their baseline score. However, this interpretation could be wrong.

Also, I'm not sure what to do if there is an NA for their baseline sum score (nothing to duplicate). This was the case for ocir for some reason: the retro scores were provided for some by not the corresponding baseline score?

@@

```{r Correlation prep chunk}
# Select items for correlation matrix
prepan_retro_items <- c(
    "gad.sum_score_prepan",
    "gad.sum_score_retro", 
    "ocir.sum_score_prepan",
    "ocir.sum_score_retro",
    "phq.sum_score_prepan",
    "phq.sum_score_retro"
)
